Data exploration

### 2021-06-03 ms/data_exploration.Rmd
Don't do dispersion test
overdispersion is so large it doesn't need it. and AER adds a bunch of deps.

# Check ratio of residual variance to df (should be near 1 to meet poisson assumptions)
richness_poisson_mod$deviance / richness_poisson_mod$df.residual

# Run statistical test
AER::dispersiontest(richness_poisson_mod, trafo=1)
```

>>>>

# Check ratio of residual variance to df (should be near 1 to meet poisson assumptions)
richness_poisson_mod$deviance / richness_poisson_mod$df.residual
```
